\documentclass{amsbook}

\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{section}{chapter}
\numberwithin{equation}{chapter}

\begin{document}

\frontmatter

\title{Minqi's Solutions to the Exercises of Sheldon Axler (2014), Linear Algebra Done Right (3rd Edition)}

\author{Minqi Pan\footnote{Website: http://www.minqi-pan.com}}

\maketitle

\setcounter{page}{4}

\tableofcontents

\chapter*{Preface}

Remarkable exercises are:
\begin{enumerate}
\item\hyperref[Exercise 1.C.13]{Exercise 1.C.13: When the Union of 3 Subspaces is a Subspace}.
\item\hyperref[Exercise 2.B.7]{Exercise 2.B.7}.
\end{enumerate}

\medskip
\begin{flushright}
Minqi Pan\\
\today
\end{flushright}

\mainmatter

\include{minqi_s_solutions_to_the_exercises_of_sheldon_axler_2014_linear_algebra_done_right_3rd_edition_ch1}

\chapter{Finite-Dimensional Vector Spaces 2.A: Span and Linear Independence}
\section{Exercise 2.A.1: Alternative Span from an Existing Span}
Suppose $v_1,v_2,v_3,v_4$ spans $V$. Prove that the list
\[
v_1-v_2,v_2-v_3,v_3-v_4,v_4
\] also spans $V$.
\begin{proof}
Denote $w_1=v_1-v_2, w_2=v_2-v_3, w_3=v_3-v_4, w_4=v_4$. Let
\[
A=\begin{bmatrix}
1& -1& 0&0\\
0& 1&-1&0\\
0& 0&1&-1\\
0& 0&0&1
\end{bmatrix},
\]
then $A$ is nonsingular and\[
A^{-1}=
\begin{bmatrix}
     1&     1&     1&     1\\
     0&     1&     1&     1\\
     0&     0&     1&     1\\
     0&     0&     0&     1
\end{bmatrix}.
\]

Moreover,\[
A\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4\end{bmatrix}=\begin{bmatrix}
w_1\\
w_2\\
w_3\\
w_4\end{bmatrix},
\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4\end{bmatrix}=A^{-1}\begin{bmatrix}
w_1\\
w_2\\
w_3\\
w_4\end{bmatrix}.
\]

\begin{enumerate}
\item Pick $x\in\text{span}(v_1,v_2,v_3,v_4)$, then there exists $x_1,x_2,x_3,x_4\in\mathbb{F}$ such that
\begin{equation*}
\begin{split}
v&=\begin{bmatrix}
x_1&x_2&x_3&x_4
\end{bmatrix}
\begin{bmatrix}v_1\\v_2\\v_3\\v_4\end{bmatrix}\\
&=\begin{bmatrix}
x_1&x_2&x_3&x_4
\end{bmatrix}
\begin{bmatrix}
     1&     1&     1&     1\\
     0&     1&     1&     1\\
     0&     0&     1&     1\\
     0&     0&     0&     1
\end{bmatrix}
\begin{bmatrix}
w_1\\
w_2\\
w_3\\
w_4\end{bmatrix}\\
&=
\begin{bmatrix}
     x_1&     x_1+x_2&     x_1+x_2+x_3&     x_1+x_2+x_3+x_4
\end{bmatrix}
\begin{bmatrix}
w_1\\
w_2\\
w_3\\
w_4
\end{bmatrix}.
\end{split}
\end{equation*}

Therefore $v\in\text{span}(w_1,w_2,w_3,w_4)$.
\item Pick $w\in\text{span}(w_1,w_2,w_3,w_4)$, then there exists $y_1,y_2,y_3,y_4\in\mathbb{F}$ such that
\begin{equation*}
\begin{split}
w&=\begin{bmatrix}
y_1&y_2&y_3&y_4
\end{bmatrix}
\begin{bmatrix}w_1\\w_2\\w_3\\w_4\end{bmatrix}\\
&=\begin{bmatrix}
y_1&y_2&y_3&y_4
\end{bmatrix}
\begin{bmatrix}
1& -1& 0&0\\
0& 1&-1&0\\
0& 0&1&-1\\
0& 0&0&1
\end{bmatrix}
\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4\end{bmatrix}\\
&=
\begin{bmatrix}
     y_1&     y_2-y_1&     y_3-y_2&     y_4-y_3
\end{bmatrix}
\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4
\end{bmatrix}.
\end{split}
\end{equation*}
Therefore $w\in\text{span}(v_1,v_2,v_3,v_4)$.
\end{enumerate}
The above (1) and (2) imply that $\text{span}(w_1,w_2,w_3,w_4)=\text{span}(v_1,v_2,v_3,v_4)$.
\end{proof}

\section{Exercise 2.A.2: Examples of Linearly Independent Lists}
Verify the assertions in Example~2.18.
\begin{enumerate}[label=(\alph*)]
\item A list $v$ of one vector $v\in V$ is linearly independent if and only if $v\ne 0$.
\item A list of two vectors in $V$ is linearly independent if and only if neither vector is a scalar multiple of the other.
\item $(1,0,0,0),(0,1,0,0),(0,0,1,0)$ is linearly independent in $\mathbb{F}^4$.
\item The list $1,z,\dots,z^m$ is linearly independent in $\mathcal{P}(\mathbb{F})$ for each nonnegative integer $m$.
\end{enumerate}
\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item If the list $v$ is linearly independent but $v=0$, then $1v=0$ is a nontrivial representation of $0$ using $v$ which is a contradiction. If $v\ne 0$ but the list $v$ is not linearly independent, then there exists $a\in\mathbb{F}$ such that $av=0$ and $a\ne 0$ which contradicts 1.30 of \cite{axler2014linear}.
\item If a list of two vectors $v_1,v_2$ in $V$ is linearly independent and assume that, without loss of generality, $v_1=av_2$ for some $a\in\mathbb{F}$, then $1v_1-av_2=0$ is a nontrivial representation of $0$ using $v_1,v_2$ which is a contradiction. If a list of two vectors $v_1,v_2$ in $V$ is not linearly independent, then there exist some $a_1,a_2\in\mathbb{F}$ such that $a_1v_1+a_2v_2=0$ and not both of $a_1$ and $a_2$ are zero. If $a_1\ne 0$, then $v_1=-\frac{a_2}{a_1}v_2$; if $a_1=0$, then $v_2=-\frac{a_1}{a_2}v_1$.
\item Consider the equation $x(1,0,0,0)+y(0,1,0,0)+z(0,0,1,0)=0$ where $x,y,z\in\mathbb{F}$. In matrix form,
\[
\begin{bmatrix}
1&0&0\\
0&1&0\\
0&0&1
\end{bmatrix}
\begin{bmatrix}
x\\
y\\
z
\end{bmatrix}
=
\begin{bmatrix}
0\\
0\\
0
\end{bmatrix}
\]
Since the coefficient matrix is nonsingular, the only solution is $x=y=z=0$.
\item Consider the function $f(z)=x_0+x_1z+\dots+x_{N-1}z^{N-1}$ where $N-1\geq 0$ and $x_0,x_1,\dots,x_{N-1}\in\mathbb{F}$. Suppose $f(z)=0$ for all $z\in\mathbb{F}$. Then, in particular, $f(1)=0, f(2)=0, \dots, f(N)=0$. In matrix form,
\[
\begin{bmatrix}
1&1&1&1&\cdots &1 \\
1&2&2^2&2^3&\cdots&2^{N-1} \\
1&3&3^2&3^3&\cdots&3^{N-1}\\
1&4&4^2&4^3&\cdots&4^{N-1}\\
\vdots&\vdots&\vdots&\vdots&\ddots&\vdots\\
1&N&N^{2}&N^{3}&\cdots&N^{N-1}
\end{bmatrix}
\begin{bmatrix}
x_0\\
x_1\\
\vdots\\
x_{N-1}
\end{bmatrix}
=
\begin{bmatrix}
0\\
0\\
\vdots\\
0
\end{bmatrix}.
\]

Note that the above coefficient matrix is a Vandermonde matrix. Since all the numbers $1, 2, \dots, N$ are distinct, its determinant is non-zero. Therefore the only solution is $x_0=x_1=\dots=x_{N-1}=0$.
\end{enumerate}
\end{proof}

\section{Exercise 2.A.3: a Linearly Dependent List}
Find a number $t$ such that
\[
(3,1,4),(2,-3,5),(5,9,t)
\]
is not linearly independent in $\mathbb{R}^3$.
\begin{proof}
We claim that $t=2$ makes the list not linearly independent in $\mathbb{R}^3$. This can be shown by
\begin{equation*}
\begin{split}
&-3\cdot (3,1,4)+2\cdot (2,-3,5)+1\cdot (5,9,2)\\
&=((-9)+4+5,(-3)+(-6)+9,(-12)+10+2)\\
&=0.
\end{split}
\end{equation*}
\end{proof}

\section{Exercise 2.A.4: Conditions to Linear Dependence}
Verify the assertion in the second bullet point in Example 2.20: the list \[(2,3,1),(1,-1,2),(7,3,c)\] is linearly dependent in $\mathbb{F}^3$ if and only if $c=8$.
\begin{proof}
Let \[
A=\begin{bmatrix}
2&1&7\\
3&-1&3\\
1&2&c
\end{bmatrix}.
\]

Then the list $(2,3,1),(1,-1,2),(7,3,c)$ is linearly dependent if and only if $\text{det}(A)=0$. Since $\text{det}(A)=40-5c$, it follows that $\text{det}(A)=0$ if and only if $c=8$.
\end{proof}

\section{Exercise 2.A.5: Difference between $\mathbb{C}$ and $\mathbb{R}$ as Scalar Fields}
\begin{enumerate}[label=(\alph*)]
\item Show that if we think of $\mathbb{C}$ as a vector space over $\mathbb{R}$, then the list $(1+i,1-i)$ is linearly independent.
\item Show that if we think of $\mathbb{C}$ as a vector space over $\mathbb{C}$, then the list $(1+i,1-i)$ is linearly dependent.
\end{enumerate}
\begin{proof}
Suppose that there exists $a+bi, c+di\in\mathbb{C}$ such that $a,b,c,d\in\mathbb{R}$ and $(a+bi)(1+i)+(c+di)(1-i)=0$, then
\[
(a-b+c+d)+(a+b-c+d)i=0,
\]

Rewrite the above linear system in the matrix form,
\[
\begin{bmatrix}
1&-1&1&1\\
1&1&-1&1
\end{bmatrix}
\begin{bmatrix}
a\\
b\\
c\\
d
\end{bmatrix}
=
\begin{bmatrix}
0\\
0
\end{bmatrix},
\]
then its solutions are
\[
\left\{\begin{bmatrix}-y\\x\\x\\y\end{bmatrix}:x,y\in\mathbb{R}\right\}.
\]

\begin{enumerate}[label=(\alph*)]
\item If we think of $\mathbb{C}$ as a vector space over $\mathbb{R}$, then the list is linearly independent because \[
\left\{\begin{bmatrix}-y\\x\\x\\y\end{bmatrix}:x,y\in\mathbb{R}\right\}\cap\left\{\begin{bmatrix}x\\0\\y\\0\end{bmatrix}:x,y\in\mathbb{R}\right\}=\left\{\begin{bmatrix}0\\0\\0\\0\end{bmatrix}\right\}.
\]
\item If we think of $\mathbb{C}$ as a vector space over $\mathbb{C}$, then the list is linearly dependent because \[
\begin{bmatrix}-1\\1\\1\\1\end{bmatrix}\in\left\{\begin{bmatrix}-y\\x\\x\\y\end{bmatrix}:x,y\in\mathbb{R}\right\}
\].
\end{enumerate}
\end{proof}

\section{Exercise 2.A.6: an Alternative Linear Independent List from an Existing List}
Suppose $v_1,v_2,v_3,v_4$ is linearly independent in $V$. Prove that the list\[
v_1-v_2,v_2-v_3,v_3-v_4,v_4
\] is also linearly independent. 
\begin{proof}
Use the same notation as the proof of Exercise~2.A.1. If the list\[
v_1-v_2,v_2-v_3,v_3-v_4,v_4
\] is linearly dependent, then there exists $a_1,a_2,a_3,a_4\in\mathbb{F}$, such that\[
\begin{bmatrix}
a_1&a_2&a_3&a_4
\end{bmatrix}
\begin{bmatrix}
w_1\\w_2\\w_3\\w_4
\end{bmatrix}
=0
\] and \[
\begin{bmatrix}
a_1&a_2&a_3&a_4
\end{bmatrix}\ne
\begin{bmatrix}
0&0&0&0
\end{bmatrix}.
\]

Therefore,\[
\begin{bmatrix}
a_1&a_2&a_3&a_4
\end{bmatrix}
A
\begin{bmatrix}
v_1\\v_2\\v_3\\v_4
\end{bmatrix}
=0.
\]

Since $A$ is nonsingular, \[
\begin{bmatrix}
a_1&a_2&a_3&a_4
\end{bmatrix}
A\ne
\begin{bmatrix}
0&0&0&0
\end{bmatrix}.
\]

Therefore it follows that the list $v_1,v_2,v_3,v_4$ is linearly dependent. 
\end{proof}

\section{Exercise 2.A.7: Another Alternative Linear Independent List from an Existing List}

Prove or give a counterexample: If $v_1,v_2,\dots,v_m$ is a linearly independent list of vectors in $V$, then\[
5v_1-4v_2,v_2,v_3,\dots,v_m
\] is linearly independent.
\begin{proof}
We claim that the proposition is true. Define \[
A=\begin{bmatrix}
5&-4&0&\dots &0\\
0&1&0&\dots &0\\
0&0&1&\dots &0\\
\vdots&\vdots&\vdots&\ddots&\vdots\\
0&0&0&\dots &1
\end{bmatrix}.
\]

Suppose that \[
5v_1-4v_2,v_2,v_3,\dots,v_m
\] is linearly dependent, then there exists $a_1,a_2,a_3,\dots,a_m\in\mathbb{F}$, such that \[
\begin{bmatrix}
a_1&a_2&a_3&\dots &a_m
\end{bmatrix}
A
\begin{bmatrix}
v_1\\v_2\\v_3\\\dots\\v_m
\end{bmatrix}
=
0
\] and \[
\begin{bmatrix}
a_1&a_2&a_3&\dots &a_m
\end{bmatrix}\ne
\begin{bmatrix}
0&0&0&\dots &0
\end{bmatrix}.
\]

Since $\text{det}(A)=5$, the matrix $A$ is nonsingular. Thus \[
\begin{bmatrix}
a_1&a_2&a_3&\dots &a_m
\end{bmatrix}A\ne
\begin{bmatrix}
0&0&0&\dots &0
\end{bmatrix}.
\]

Therefore it follows that the list $v_1,v_2,\dots,v_m$ is linearly dependent.
\end{proof}

\section{Exercise 2.A.8: Linear Independent List Multiplied by Scalar}
Prove or give a counterexample: If $v_1,v_2,\dots,v_m$ is a linearly independent list of vectors in $V$ and $\lambda\in\mathbb{F}$ with $\lambda\ne 0$, then $\lambda v_1,\lambda v_2,\dots,\lambda v_m$ is linearly independent.
\begin{proof}
We claim that the proposition is true. Suppose that $\lambda v_1,\lambda v_2,\dots,\lambda v_m$ is linearly dependent, then there exists $a_1,a_2,\dots,a_m$, not all $0$, such that\[
a_1\lambda v_1+a_2\lambda v_2+\dots+a_m\lambda v_m=0.
\]

Since $\lambda\ne 0$, $\lambda^{-1}$ exists in $\mathbb{F}$. Multiplying the above equation by $\lambda^{-1}$ yields \[
a_1 v_1+a_2 v_2+\dots+a_m v_m=0.
\]

Note that not all of $a_1, a_2,\dots,a_m$ are zero. Therefore it follows that $v_1,v_2,\dots,v_m$ is a linearly dependent list.
\end{proof}

\section{Exercise 2.A.9: Addition of Two Linearly Independent Lists}
Prove or give a counterexample: If $v_1,\dots,v_m$ and $w_1,\dots,w_m$ are linearly independent lists of vectors in $V$, then $v_1+w_1,\dots,v_m+w_m$ is linearly independent.
\begin{proof}[Counterexample]
Set $V=\mathbb{R}^2, m=2, v_1=(0,1), v_2=(1,0), w_1=(0,-1), w_2=(-1,0)$. Then $v_1, v_2$ is a linearly independent list, and $w_1, w_2$ is also a linearly independent list. But\[
v_1+w_1=(0,0)
\] and \[
v_2+w_2=(0,0)
\] is not a linearly independent list.
\end{proof}

\section{Exercise 2.A.10: Adding a Vector to a Linearly Independent List}
Suppose $v_1,\dots,v_m$ is linearly independent in $V$ and $w\in V$. Prove that if $v_1+w,\dots,v_m+w$ is linearly dependent, then $w\in \text{span}(v_1,\dots,v_m)$.
\begin{proof}
If $v_1+w,\dots,v_m+w$ is linearly dependent, then there exists $a_1,\dots,a_m$, not all $0$, such that\[
a_1(v_1+w)+\dots+a_m(v_m+w)=0.
\]

The above equation implies that\[
w=-\frac{a_1}{a_1+\dots+a_m}v_1-\dots-\frac{a_m}{a_1+\dots+a_m}v_m,
\]
thus $w\in\text{span}(v_1,\dots,v_m)$.
\end{proof}

\section{Exercise 2.A.11: Concatenating a Vector to a Linearly Independent List}
Suppose $v_1,\dots,v_m$ is linearly independent in $V$ and $w\in V$. Show that $v_1,\dots,v_m,w$ is linearly independent if and only if\[
w\notin \text{span}(v_1,\dots,v_m).
\]
\begin{proof}
\begin{enumerate}
\item Suppose that $v_1,\dots,v_m,w$ is linearly dependent, then there exists $a_1,\dots,a_m,a_w\in\mathbb{F}$, not all $0$, such that\[
a_1v_1+\dots+a_mv_m+a_ww=0.
\]

If $a_w=0$, then the above equation would imply that $v_1,\dots,v_m$ is linearly dependent, which is a contradiction. Therefore $a_w\ne 0$ and the above equation implies that\[
w=-\frac{a_1}{a_w}v_1-\dots-\frac{a_m}{a_w}v_m.
\]

Thus $w\in \text{span}(v_1,\dots,v_m)$.
\item Suppose that $w\in \text{span}(v_1,\dots,v_m)$, then there exists $a_1,\dots,a_m\in\mathbb{F}$ such that\[
w=a_1v_1+\dots+a_mv_m.
\]

The above equation implies that\[
a_1v_1+\dots+a_mv_m-w=0.
\]

Thus $v_1,\dots,v_m,w$ is linearly dependent.
\end{enumerate}
\end{proof}

\section{Exercise 2.A.12: Possible Linearly Independent Lists in $\mathcal{P}_4(\mathbb{F})$}
Explain why there does not exist a list of six polynomials that is linearly independent in $\mathcal{P}_4(\mathbb{F})$.
\begin{proof}
It is obvious that the list $1, z, z^2, z^3, z^4$ spans $\mathcal{P}_4(\mathbb{F})$, which has length $5$. By 2.23 of \cite{axler2014linear}, the length of every linearly independent list of vectors in $\mathcal{P}_4(\mathbb{F})$ is therefore less than or equal to $5$. Thus there does not exist a list of $6$ polynomials that is linearly independent in $\mathcal{P}_4(\mathbb{F})$.
\end{proof}

\section{Exercise 2.A.13: Possible Spans of $\mathcal{P}_4(\mathbb{F})$}
Explain why no list of four polynomials spans $\mathcal{P}_4(\mathbb{F})$.
\begin{proof}
Exercise 2.A.2 (d) has already proved that the list $1, z, z^2, z^3, z^4$ is linearly independent in $\mathcal{P}_4(\mathbb{F})$, which has length $5$. By 2.23 of \cite{axler2014linear}, the length of every spanning list of $\mathcal{P}_4(\mathbb{F})$ is greater than or equal to $5$. Thus no list of $4$ polynomials spans $\mathcal{P}_4(\mathbb{F})$.
\end{proof}

\section{Exercise 2.A.14: Another Definition of Infinite-Dimensional}
Prove that $V$ is infinite-dimensional if and only if there is a sequence $v_1,v_2,\dots$ of vectors in $V$ such that $v_1,\dots,v_m$ is linearly independent for every positive integer $m$.
\begin{proof}
\begin{enumerate}
\item Suppose that $V$ is finite-dimensional, then there exists a list $u_1,\dots,u_k$ in $V$ that spans $V$. By 2.23 of \cite{axler2014linear}, the length of every linearly independent list of vectors in $V$ is less than or equal to $k$. Therefore, if we pick any vector sequence $v_1,v_2,\dots$ in $V$, $v_1,\dots,v_{k+1}$ must be linearly dependent.

\item Suppose that $V$ is infinite-dimensional. We can construct, by the following steps, a sequence $v_1,v_2,\dots$ of vectors in $V$ such that $v_1,\dots,v_m$ is linearly independent for every positive integer $m$:
\begin{enumerate}
\item[Step (1):] Pick any $v\in V$ such that $v\ne 0$, and let $v_1=v$. Note that the list $v_1$ is linearly independent.
\item[Step ($n$):] Suppose that Step ($n-1$) has already created a vector list $v_1,\dots,v_{n-1}$ such that $v_1,\dots,v_m$ is linearly independent for every positive integer $m\in\{1,\dots,n-1\}$. Since $V$ is infinite-dimensional, there exists $w\in V$ such that $w\notin \text{span}(v_1,\dots,v_{n-1})$. Set $v_n=w$, and we claim that $v_1,\dots,v_n$ is linearly independent. To prove this, suppose that there exists $a_1,\dots,a_n\in\mathbb{F}$, not all zero, such that\[
a_1v_1+\dots+a_nv_n=0.
\]
If $a_n=0$, then $a_1,\dots,a_{n-1}$ would be linearly dependent, which is a contradiction. If $a_n\ne 0$, then\[
v_n=-\frac{a_1}{a_n}v_1-\dots-\frac{a_{n-1}}{a_n}v_{n-1},
\] which implies that $v_n\in\text{span}(v_1,\dots,u_{n-1})$, which is also a contradiction.
\end{enumerate}
\end{enumerate}
\end{proof}

\section{Exercise 2.A.15: $\mathbb{F}^\infty$ is Infinite-Dimensional}
Prove that $\mathbb{F}^\infty$ is infinite-dimensional.
\begin{proof}
Suppose that $\mathbb{F}^\infty$ is finite-dimensional, then there exists a list $v_1,\dots,v_k\in\mathbb{F}^\infty$ such that $\mathbb{F}^\infty=\text{span}(v_1,\dots,v_k)$. But we may construct the following independent list of vectors in $\mathbb{F}^\infty$ which has length $k+1$, contradicting with 2.23 of \cite{axler2014linear}.
\begin{equation*}
\begin{split}
v_1&=(1, 0, 0, \dots, 0, 0, 0, 0, \dots)\\
v_2&=(0, 1, 0, \dots, 0, 0, 0, 0, \dots)\\
v_3&=(0, 0, 1, \dots, 0, 0, 0, 0, \dots)\\
\vdots&\\
v_{k-1}&=(0, 0, 0, \dots, 1, 0, 0, 0, \dots)\\
v_k&=(0, 0, 0, \dots, 0, 1, 0, 0, \dots)\\
v_{k+1}&=(0, 0, 0, \dots, 0, 0, 1, 0, \dots)
\end{split}
\end{equation*}
\end{proof}

\section{Exercise 2.A.16: $\mathbb{R}^{[0,1]}$ is Infinite-Dimensional}
Prove that the real vector space of all continuous real-valued functions
on the interval $[0,1]$ is infinite-dimensional.
\begin{proof}
Suppose that $\mathbb{R}^{[0,1]}$ is finite-dimensional, then there exists a list \[
v_1,\dots,v_k\in\mathbb{R}^{[0,1]}
\] such that $\mathbb{R}^{[0,1]}=\text{span}(v_1,\dots,v_k)$. But we may construct the following independent list of vectors in $\mathbb{R}^{[0,1]}$ which has length $k+1$, contradicting with 2.23 of \cite{axler2014linear}.
\begin{equation*}
\begin{split}
v_1(x)&=1\text{ if }x=\frac{1}{k+2}\text{; otherwise }0\\
v_2(x)&=1\text{ if }x=\frac{2}{k+2}\text{; otherwise }0\\
v_3(x)&=1\text{ if }x=\frac{3}{k+2}\text{; otherwise }0\\
\vdots&\\
v_{k-1}(x)&=1\text{ if }x=\frac{k-1}{k+2}\text{; otherwise }0\\
v_k(x)&=1\text{ if }x=\frac{k}{k+2}\text{; otherwise }0\\
v_{k+1}(x)&=1\text{ if }x=\frac{k+1}{k+2}\text{; otherwise }0.
\end{split}
\end{equation*}
\end{proof}

\section{Exercise 2.A.17: Polynomials that Vanish at the Same Point}
Suppose $p_0, p_1,\dots, p_m$ are polynomials in $\mathcal{P}_m(\mathbb{F})$ such that $p_j(2)=0$ for each $j$. Prove that $p_0, p_1,\dots, p_m$ is not linearly independent in $\mathcal{P}_m(\mathbb{F})$.
\begin{proof}
Denote $p_j(z)=a_{j0}+a_{j1}z+a_{j2}z^2+\dots+a_{jm}z^m$ for each $j$ and let\[
A=\begin{bmatrix}
a_{00} & a_{01} & a_{02} & \dots & a_{0m}\\
a_{00} & a_{01} & a_{02} & \dots & a_{0m}\\
\vdots & \vdots  & \vdots & \ddots &\vdots\\
a_{m0} & a_{m1} & a_{m2} & \dots & a_{mm}
\end{bmatrix}.
\]

That $p_j(2)=0$ for each $j$ implies\[
A\begin{bmatrix}
2^0\\
2^1\\
2^2\\
\vdots\\
2^m
\end{bmatrix}=\begin{bmatrix}
0\\
0\\
0\\
\vdots\\
0
\end{bmatrix}.
\]

Thus $A$ is a singular matrix, and so is $A^T$.

Suppose there exists $s_0,s_1,\dots,s_m\in\mathbb{F}$ such that $s_0p_0+s_1p_1+\dots+s_mp_m=0$, then\[
\begin{bmatrix}
a_{00} & a_{10} & \dots & a_{m0}\\
a_{01} & a_{11} & \dots & a_{m1}\\
\vdots  & \vdots & \ddots &\vdots\\
a_{0m} & a_{1m} & \dots & a_{mm}\\
\end{bmatrix}
\begin{bmatrix}
s_0\\
s_1\\
\vdots\\
s_m
\end{bmatrix}=\begin{bmatrix}
0\\
0\\
\vdots\\
0
\end{bmatrix}.
\]

Note that the coefficient matrix of the above linear system is $A^T$, which we have shown is a singular matrix. So the linear system has a nonzero solution. We therefore conclude that the list $p_0,p_1,\dots,p_m$ is linearly dependent.
\end{proof}

\chapter{Finite-Dimensional Vector Spaces 2.B: Bases}
\section{Exercise 2.B.1}
Find all vector spaces that have exactly one basis.
\begin{proof}
We claim that no vector spaces over $\mathbb{F}$ (which is either $\mathbb{R}$ or $\mathbb{C}$) have exactly one basis.

Given a vector space $V$. Suppose that $v_1,\dots,v_k$ is the only basis of $V$. Denote \[
v=\begin{bmatrix}
v_1\\
\vdots\\
v_k\end{bmatrix}.\]

Note that $Av$ is also a basis of $V$ for any nonsingular matrix $A$, then\[
Av=v\text{, for all nonsingular }A.
\]

In particular, take $A=2I$. Then\[
(2I-I)v=0,
\] which implies that $v=0$. But the list $0$ is not linearly dependent, contradicting with the presumption that $v_1,\dots,v_k$ is a basis.
\end{proof}

\section{Exercise 2.B.2}
Verify all the assertions in Example 2.28.
\begin{enumerate}[label=(\alph*)]
\item The list $(1,0,\dots,0),(0,1,0,\dots,0),\dots,(0,\dots,0,1)$ is a basis of $\mathbb{F}^n$,
called the standard basis of $\mathbb{F}^n$.
\item The list $(1, 2), (3,5)$ is a basis of $\mathbb{F}^2$.
\item The list $(1, 2, -4), (7,-5, 6)$ is linearly independent in $\mathbb{F}^3$ but is not a basis of $\mathbb{F}^3$ because it does not span $\mathbb{F}^3$.
\item The list $(1, 2), (3, 5), (4, 13)$ spans $\mathbb{F}^2$ but is not a basis of $\mathbb{F}^2$ because it is not linearly independent.
\item The list $(1,1,0),(0,0,1)$ is a basis of $\{(x,x,y)\in\mathbb{F}^3:x,y\in\mathbb{F}\}$.
\item The list $(1,-1,0),(1,0,-1)$ is a basis of\[
\{(x,y,z)\in\mathbb{F}^3: x+y+z=0\}.
\]
\item The list $1,z,\dots,z^m$ is a basis of $\mathcal{P}_m(\mathbb{F})$.
\end{enumerate}
\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item Pick $v=(v_1,v_2,\dots,v_n)\in\mathbb{F}^n$ where $v_1,v_2,\dots,v_n\in\mathbb{F}$. Then it is obvious that $v$ can be written uniquely as\[
v_1(1,0,\dots,0)+v_2(0,1,0,\dots,0)+\dots+v_n(0,\dots,0,1).
\]
\item Pick $v=(v_1,v_2)\in\mathbb{F}^2$. Let $v=x(1, 2)+y(3,5)$ where $x,y\in\mathbb{F}$, which corresponds to the following linear system\[
\begin{bmatrix}
1&3\\
2&5
\end{bmatrix}
\begin{bmatrix}
x\\
y
\end{bmatrix}
=
\begin{bmatrix}
v_1\\
v_2
\end{bmatrix}.
\]

Since the coefficient of the above linear system is nonsingular, there is exactly one solution $\begin{bmatrix}x&y\end{bmatrix}^T$ for every $\begin{bmatrix}v_1&v_2\end{bmatrix}^T$. Therefore $(1,2),(3,5)$ is a basis of $\mathbb{F}^2$.
\item As shown in (1), there exists a linearly independent list of length $3$ in $\mathbb{F}^3$, thus no lists of length $2$ can span $\mathbb{F}^3$ by 2.23 of \cite{axler2014linear}.
\item As shown in (1), there exists a list of length $2$ that spans $\mathbb{F}^2$, thus no lists of length $3$ can be linearly independent in $\mathbb{F}^2$ by 2.23 of \cite{axler2014linear}.
\item Pick $v=(x,x,y)\in\mathbb{F}^3$ where $x,y\in\mathbb{F}$. Then it is obvious that $v$ can be written uniquely as\[
x(1,1,0)+y(0,0,1).
\]
\item Denote $V=\{(x,y,z)\in\mathbb{F}^3: x+y+z=0\}$. Pick $v=(a,b,c)\in V$ then $c=-a-b$. Let $v=x(1,-1,0)+y(1,0,-1)$ where $x,y\in\mathbb{F}$, which corresponds to the following linear system\[
\begin{bmatrix}
1&1\\
-1&0\\
0&-1
\end{bmatrix}
\begin{bmatrix}
x\\
y\\
\end{bmatrix}
=
\begin{bmatrix}
a\\
b\\
-a-b
\end{bmatrix}.
\]

Note that the above linear system is an overdetermined system, so it has either no solutions or a unique solution. Moreover, it can be shown that \[
\begin{bmatrix}-b\\
a+b\end{bmatrix}
\] is one possible solution. Therefore every $v\in V$ can be written uniquely using $(1,-1,0),(1,0,-1)$.
\item Pick $v(z)=a_0+a_1z+a_2z^2+\dots+a_mz^m\in\mathcal{P}_m(\mathbb{F})$ where $a_0,a_1,a_2,\dots,a_m\in\mathbb{F}$. Then 4.7 of \cite{axler2014linear} implies that $v$ can be written uniquely as\[
a_0\cdot 1+a_1\cdot z+a_2\cdot z^2+\dots+a_m\cdot z^m.
\]
\end{enumerate}
\end{proof}

\section{Exercise 2.B.3}
\begin{enumerate}[label=(\alph*)]
\item Let $U$ be the subspace of $\mathbb{R}^5$ defined by\[
U=\{(x_1,x_2,x_3,x_4,x_5)\in\mathbb{R}^5:x_1=3x_2\text{ and }x_3=7x_4\}.
\]
Find a basis of $U$.
\item Extend the basis in part (a) to a basis of $\mathbb{R}^5$.
\item Find a subspace $W$ of $\mathbb{R}^5$ such that $\mathbb{R}^5=U\oplus W$.
\end{enumerate}
\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item Let
\begin{equation*}
\begin{split}
u_1&=(3,1,0,0,0)\\
u_2&=(0,0,7,1,0)\\
u_3&=(0,0,0,0,1).
\end{split}
\end{equation*}

We claim that the list $u_1,u_2,u_3$ is a basis of $U$. To prove this, pick $u=(x_1,x_2,x_3,x_4,x_5)\in U$, then it is obvious that $u$ can be uniquely represented as\[
x_2u_1+x_4u_2+x_5u_3.
\]
\item Let
\begin{equation*}
\begin{split}
v_1&=(1,0,0,0,0)\\
v_2&=(0,1,0,0,0)\\
v_3&=(0,0,1,0,0)\\
v_4&=(0,0,0,1,0)\\
v_5&=(0,0,0,0,1).
\end{split}
\end{equation*}

Then $v_1,v_2,v_3,v_4,v_5$ is a basis of $\mathbb{R}^5$. Thus the list\[
u_1,u_2,u_3,v_1,v_2,v_3,v_4,v_5
\] spans $\mathbb{R}^5$. The procedure of the proof of 2.31 of \cite{axler2014linear} deletes $v_2,v_4,v_5$ and leaves $v_1,v_3$ unchanged, resulting in the following basis of $\mathbb{R}^5$ extended from the basis in part (a):
\[
u_1,u_2,u_3,v_1,v_3.
\]
\item Let $W=\text{span}(v_1,v_3)$. We claim that $\mathbb{R}^5=U\oplus W$. To prove this, by 1.45 of \cite{axler2014linear}, we only need to show that\[
\mathbb{R}^5=U+W\text{ and }U\cap W=\{0\}.
\]

To prove the 1st equation above, suppose $v\in \mathbb{R}^5$. Then because the list $u_1,u_2,u_3,v_1,v_3$ spans $\mathbb{R}^5$, there exists $a_1,a_2,a_3,b_1,b_3\in\mathbb{F}$ such that\[
v=a_1u_1+a_2u_2+a_3u_3+b_1v_1+b_3v_3.
\]

In other words, we have $v=u+w$, where $u=(a_1u_1+a_2u_2+a_3u_3)\in U$ and $w=(b_1v_1+b_3v_3)\in W$. Thus $v\in U+W$, completing the proof that $\mathbb{R}^5=U+W$.

To show that $U\cap W=\{0\}$, suppose $v\in U\cap W$. Then there exist scalars $a_1,a_2,a_3,b_1,b_3\in\mathbb{F}$ such that\[
v= a_1u_1+a_2u_2+a_3u_3=b_1v_1+b_3v_3.
\]

Thus\[
a_1u_1+a_2u_2+a_3u_3-b_1v_1-b_3v_3=0.
\]

Because $u_1,u_2,u_3,v_1,v_3$ is linearly independent, this implies that $a_1=a_2=a_3=b_1=b_3=0$. Thus $v=0$, completing the proof that $U\cap W=\{0\}$.
\end{enumerate}
\end{proof}

\section{Exercise 2.B.4}
\begin{enumerate}[label=(\alph*)]
\item Let $U$ be the subspace of $\mathbb{C}^5$ defined by\[
U=\{(z_1,z_2,z_3,z_4,z_5)\in\mathbb{C}^5:6z_1=x_2\text{ and }z_3+2z_4+3z_5=0\}.
\]
Find a basis of $U$.
\item Extend the basis in part (a) to a basis of $\mathbb{C}^5$.
\item Find a subspace $W$ of $\mathbb{C}^5$ such that $\mathbb{C}^5=U\oplus W$.
\end{enumerate}

\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item Let
\begin{equation*}
\begin{split}
u_1&=(1,6,0,0,0)\\
u_2&=(0,0,-2,1,0)\\
u_3&=(0,0,-3,0,1).
\end{split}
\end{equation*}

We claim that the list $u_1,u_2,u_3$ is a basis of $U$. To prove this, pick $u=(z_1,z_2,z_3,z_4,z_5)\in U$, then it is obvious that $u$ can be uniquely represented as\[
x_1u_1+x_4u_2+x_5u_3.
\]
\item Let
\begin{equation*}
\begin{split}
v_1&=(1,0,0,0,0)\\
v_2&=(0,1,0,0,0)\\
v_3&=(0,0,1,0,0)\\
v_4&=(0,0,0,1,0)\\
v_5&=(0,0,0,0,1).
\end{split}
\end{equation*}

Then $v_1,v_2,v_3,v_4,v_5$ is a basis of $\mathbb{C}^5$. Thus the list\[
u_1,u_2,u_3,v_1,v_2,v_3,v_4,v_5
\] spans $\mathbb{C}^5$. The procedure of the proof of 2.31 of \cite{axler2014linear} deletes $v_2,v_4,v_5$ and leaves $v_1,v_3$ unchanged, resulting in the following basis of $\mathbb{C}^5$ extended from the basis in part (a):
\[
u_1,u_2,u_3,v_1,v_3.
\]
\item Let $W=\text{span}(v_1,v_3)$. We claim that $\mathbb{C}^5=U\oplus W$. To prove this, by 1.45 of \cite{axler2014linear}, we only need to show that\[
\mathbb{C}^5=U+W\text{ and }U\cap W=\{0\}.
\]

To prove the 1st equation above, suppose $v\in \mathbb{C}^5$. Then because the list $u_1,u_2,u_3,v_1,v_3$ spans $\mathbb{C}^5$, there exists $a_1,a_2,a_3,b_1,b_3\in\mathbb{F}$ such that\[
v=a_1u_1+a_2u_2+a_3u_3+b_1v_1+b_3v_3.
\]

In other words, we have $v=u+w$, where $u=(a_1u_1+a_2u_2+a_3u_3)\in U$ and $w=(b_1v_1+b_3v_3)\in W$. Thus $v\in U+W$, completing the proof that $\mathbb{C}^5=U+W$.

To show that $U\cap W=\{0\}$, suppose $v\in U\cap W$. Then there exist scalars $a_1,a_2,a_3,b_1,b_3\in\mathbb{F}$ such that\[
v= a_1u_1+a_2u_2+a_3u_3=b_1v_1+b_3v_3.
\]

Thus\[
a_1u_1+a_2u_2+a_3u_3-b_1v_1-b_3v_3=0.
\]

Because $u_1,u_2,u_3,v_1,v_3$ is linearly independent, this implies that $a_1=a_2=a_3=b_1=b_3=0$. Thus $v=0$, completing the proof that $U\cap W=\{0\}$.
\end{enumerate}
\end{proof}

\section{Exercise 2.B.5}
Prove or disprove: there exists a basis $p_0,p_1,p_2,p_3$ of $\mathcal{P}_3(\mathbb{F})$ such that none of the polynomials $p_0,p_1,p_2,p_3$ has degree $2$.
\begin{proof}
We claim that the following list is a possible choice of such $p_0,p_1,p_2,p_3$:
\begin{equation*}
\begin{split}
p_0(z)&=1+z^3\\
p_1(z)&=z+z^3\\
p_2(z)&=z^2+z^3\\
p_3(z)&=z^3.
\end{split}
\end{equation*}

To prove this, note that $p_0,p_1,p_2,p_3$ each has degree $3$. Thus it only suffices to show that $p_0,p_1,p_2,p_3$ is a basis of $\mathcal{P}_3(\mathbb{F})$.

Pick $p(z)\in \mathcal{P}_3(\mathbb{F})$. As shown in Exercise 2.B.2, $1,z,z^2,z^3$ is a basis $\mathcal{P}_3(\mathbb{F})$. Thus there exists a unique list of scalars $a_0,a_1,a_2,a_3\in\mathbb{F}$ such that\[
p(z)=a_0+a_1z+a_2z^2+a_3z^3.
\]

Let us denote \[
A=\begin{bmatrix}
1&0&0&1\\
0&1&0&1\\
0&0&1&1\\
0&0&0&1
\end{bmatrix},
\]then $A$ is a nonsingular matrix and\[
A^{-1}=\begin{bmatrix}
1&0&0&-1\\
0&1&0&-1\\
0&0&1&-1\\
0&0&0&1
\end{bmatrix}.
\]

Using this notation, we have\[
\begin{bmatrix}
p_0\\
p_1\\
p_2\\
p_3
\end{bmatrix}
=
A\begin{bmatrix}
1\\
z\\
z^2\\
z^3
\end{bmatrix},
\] and \[
A^{-1}
\begin{bmatrix}
p_0\\
p_1\\
p_2\\
p_3
\end{bmatrix}
=
\begin{bmatrix}
1\\
z\\
z^2\\
z^3
\end{bmatrix}.
\]

Therefore
\begin{equation*}
\begin{split}
p(z)&=\begin{bmatrix}a_0&a_1&a_2&a_3\end{bmatrix}
\begin{bmatrix}
1\\
z\\
z^2\\
z^3
\end{bmatrix}\\
&=\left(\begin{bmatrix}a_0&a_1&a_2&a_3\end{bmatrix}A^{-1}\right)
\begin{bmatrix}
p_0\\
p_1\\
p_2\\
p_3
\end{bmatrix}.
\end{split}
\end{equation*}

The above equation implies that $p_0,p_1,p_2,p_3$ spans $\mathcal{P}_3(\mathbb{F})$.

To show that $p_0,p_1,p_2,p_3$ is linearly independent, suppose $b_0,b_1,b_2,b_3\in\mathbb{F}$ are such that
\[
0=\begin{bmatrix}b_0&b_1&b_2&b_3\end{bmatrix}
\begin{bmatrix}
p_0\\
p_1\\
p_2\\
p_3
\end{bmatrix}.
\]

Then the above equation implies that\[
0=\left(\begin{bmatrix}b_0&b_1&b_2&b_3\end{bmatrix}
A\right)\begin{bmatrix}
1\\
z\\
z^2\\
z^3
\end{bmatrix}.
\]

Since $1,z,z^2,z^3$ is linearly independent, this implies that\[
0=\begin{bmatrix}b_0&b_1&b_2&b_3\end{bmatrix}A.
\]

Since $A$ is nonsingular, this further implies that\[
0=\begin{bmatrix}b_0&b_1&b_2&b_3\end{bmatrix}.
\]

Thus $p_0,p_1,p_2,p_3$ is linearly independent and hence is a basis of $\mathcal{P}_3(\mathbb{F})$.
\end{proof}

\section{Exercise 2.B.6}
Suppose $v_1,v_2,v_3,v_4$ is a basis of $V$. Prove that\[
v_1+v_2,v_2+v_3,v_3+v_4,v_4
\] is also a basis of $V$.
\begin{proof}
Denote 
\begin{equation*}
\begin{split}
u_1&=v_1+v_2\\
u_2&=v_2+v_3\\
u_3&=v_3+v_4\\
u_4&=v_4.
\end{split}
\end{equation*}

Pick $v\in V$, then there exists a unique list of scalars $a_1,a_2,a_3,a_4\in\mathbb{F}$ such that\[
v=a_1v_1+a_2v_2+a_3v_3+a_4v_4.
\]

Let us denote \[
A=\begin{bmatrix}
1&1&0&0\\
0&1&1&0\\
0&0&1&1\\
0&0&0&1
\end{bmatrix},
\]then $A$ is a nonsingular matrix and\[
A^{-1}=\begin{bmatrix}
1&-1&1&-1\\
0&1&-1&1\\
0&0&1&-1\\
0&0&0&1
\end{bmatrix}.
\]

Using this notation, we have\[
\begin{bmatrix}
u_1\\
u_2\\
u_3\\
u_4
\end{bmatrix}
=
A\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4
\end{bmatrix},
\] and \[
A^{-1}
\begin{bmatrix}
u_1\\
u_2\\
u_3\\
u_4
\end{bmatrix}
=
\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4
\end{bmatrix}.
\]

Therefore
\begin{equation*}
\begin{split}
v&=\begin{bmatrix}a_0&a_1&a_2&a_3\end{bmatrix}
\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4
\end{bmatrix}\\
&=\left(\begin{bmatrix}a_0&a_1&a_2&a_3\end{bmatrix}A^{-1}\right)
\begin{bmatrix}
u_1\\
u_2\\
u_3\\
u_4
\end{bmatrix}.
\end{split}
\end{equation*}

The above equation implies that $u_1,u_2,u_3,u_4$ spans $V$.

To show that $u_1,u_2,u_3,u_4$ is linearly independent, suppose $b_1,b_2,b_3,b_4\in\mathbb{F}$ are such that
\[
0=\begin{bmatrix}b_1&b_2&b_3&b_4\end{bmatrix}
\begin{bmatrix}
u_1\\
u_2\\
u_3\\
u_4
\end{bmatrix}.
\]

Then the above equation implies that\[
0=\left(\begin{bmatrix}b_1&b_2&b_3&b_4\end{bmatrix}
A\right)\begin{bmatrix}
v_1\\
v_2\\
v_3\\
v_4
\end{bmatrix}.
\]

Since $v_1,v_2,v_3,v_4$ is linearly independent, this implies that\[
0=\begin{bmatrix}b_1&b_2&b_3&b_4\end{bmatrix}A.
\]

Since $A$ is nonsingular, this further implies that\[
0=\begin{bmatrix}b_1&b_2&b_3&b_4\end{bmatrix}.
\]

Thus $u_1,u_2,u_3,u_4$ is linearly independent and hence is a basis of $V$.
\end{proof}

\section{Exercise 2.B.7}\label{Exercise 2.B.7}
Prove or give a counterexample: If $v_1, v_2, v_3, v_4$ is a basis of $V$ and $U$ is a subspace of $V$ such that $v_1, v_2\in U$ and $v_3\notin U$ and $v_4\notin U$, then $v_1, v_2$ is a basis of $U$.
\begin{proof}[Counterexample]
Take $V=\mathbb{R}^4$ and define
\begin{equation*}
\begin{split}
v_1&=(2,0,1,0),\\
v_2&=(0,0,0,1),\\
v_3&=(0,3,\frac{1}{2},1),\\
v_4&=(3,0,1,\frac{1}{2}).
\end{split}
\end{equation*}

We claim that $v_1,v_2,v_3,v_4$ is a basis of $V$, which can be shown by the following determinant calculation:\[
\text{det}\left(
\begin{matrix}
2&0&1&0\\
0&0&0&1\\
0&3&\frac{1}{2}&1\\
3&0&1&\frac{1}{2}
\end{matrix}
\right)=-3.
\]

Define\[
U=\{(2x,y,x,z)\in\mathbb{R}^4:x,y,z\in\mathbb{R}\}.
\]

We claim that $U$ is a subspace of $V$. To show this, first $0=(2\cdot 0,0,0,0)$ is in $U$. Suppose $u=(2x,y,x,z)\in U$ and $w=(2a,b,a,c)\in U$, we can check that $u+w=(2x+2a,y+b,x+a,z+c)=(2(x+a),y+b,x+a,z+c)$ is in $U$. Suppose $f\in\mathbb{F}$ and $u=(2x,y,x,z)\in U$, we can check that $fu=(2fx,y,fx,z)=(2(fx),y,fx,z)$ is also in $U$.

Further, it is clear that $v_1,v_2\in U, v_3\notin U, v_4\notin U$.

Finally, since $(0,1,0,0)\in U$ cannot be written as a linear combination of $v_1$ and $v_2$, we conclude that $v_1,v_2$ is not a basis of $U$.
\end{proof}

\section{Exercise 2.B.8}
Suppose $U$ and $W$ are subspaces of $V$ such that $V=U\oplus W$. Suppose also that $u_1,\dots,u_m$ is a basis of $U$ and $w_1,\dots,w_n$ is a basis of $W$. Prove that \[
u_1,\dots,u_m,w_1,\dots,w_n
\] is a basis of $V$.
\begin{proof}
\begin{enumerate}
\item We first prove that $u_1,\dots,u_m,w_1,\dots,w_n$ spans $V$.
Pick $v\in V$. By the definition of direct sum, $v$ can be written in the only one way as a sum $u+w$, where $u\in U$ and $w\in W$. By the definition of basis, $u$ can be written as $u=a_1u_1+\dots+a_mu_m$ and $w$ can be written as $w=b_1w_1+\dots+b_nw_n$ where $a_1,\dots,a_m,b_1,\dots,b_n\in\mathbb{F}$. Taken together,\[
v=a_1u_1+\dots+a_mu_m+b_1w_1+\dots+b_nw_n.
\]
\item We then prove that $u_1,\dots,u_m,w_1,\dots,w_n$ is linearly independent.
Suppose there exist $x_1,\dots,x_m,y_1,\dots,y_n\in\mathbb{F}$ such that\[
x_1u_1+\dots+x_mu_m+y_1w_1+\dots+y_nw_n=0.
\] Then\[
x_1u_1+\dots+x_mu_m=-y_1w_1-\dots-y_nw_n.
\] Denote $p=x_1u_1+\dots+x_mu_m$ and $q=-y_1w_1-\dots-y_nw_n$, then $p\in U\cap W$ and $q\in U\cap W$. By 1.45 of \cite{axler2014linear}, $p=q=0$.

Further, since $u_1,\dots,u_m$ is linearly independent, $p=0$ implies that all of $x_1,\dots,x_m$ are $0$. Similarly, since $w_1,\dots,w_n$ is linearly independent, $q=0$ implies that all of $y_1,\dots,y_n$ are $0$.
\end{enumerate}
\end{proof}

\chapter{Finite-Dimensional Vector Spaces 2.C: Dimension}
\section{Exercise 2.C.1}
Suppose $V$ is finite-dimensional and $U$ is a subspace of $V$ such that $\dim U=\dim V$. Prove that $U=V$.
\begin{proof}
Suppose $\dim U=\dim V=n$ and $u_1,\dots,u_n$ is a basis of $U$. Since $u_1,\dots,u_n$ is a linearly independent list in $V$ with length $\dim V$, 2.39 of \cite{axler2014linear} implies that $u_1,\dots,u_n$ is a basis of $V$. Hence\[
U=\text{span}(u_1,\dots,u_n)=V.
\]
\end{proof}

\section{Exercise 2.C.2}
Show that the subspaces of $\mathbb{R}^2$ are precisely $\{0\}$, $\mathbb{R}^2$, and all lines in $\mathbb{R}^2$ through the origin.
\begin{proof}
Pick a subspace $U$ of $\mathbb{R}^2$, then $\dim U\in\{0,1,2\}$ by 2.39 of \cite{axler2014linear}.
\begin{enumerate}
\item If $\dim U=0$, then $U=\{0\}$.
\item If $\dim U=1$, then there exists a vector $v=(x,y)\in\mathbb{R}^2$ such that\[
U=\text{span}(v).
\]Hence, geometrically, $U$ can be viewed as a line in $\mathbb{R}^2$ passing through points $(0,0)$ and $(x,y)$.
\item If $\dim U=2$, then Exercise 2.C.1 implies that $U=\mathbb{R}^2$.
\end{enumerate}
\end{proof}

\section{Exercise 2.C.3}
Show that the subspaces of $\mathbb{R}^3$ are precisely $\{0\}$, $\mathbb{R}^3$, all lines in $\mathbb{R}^3$ through the origin, and all planes in $\mathbb{R}^3$ through the origin.
\begin{proof}
Pick a subspace $U$ of $\mathbb{R}^3$, then $\dim U\in\{0,1,2,3\}$ by 2.39 of \cite{axler2014linear}.
\begin{enumerate}
\item If $\dim U=0$, then $U=\{0\}$.
\item If $\dim U=1$, then there exists a vector $v=(x,y,z)\in\mathbb{R}^3$ such that\[
U=\text{span}(v).
\]Hence, geometrically, $U$ can be viewed as a line in $\mathbb{R}^3$ passing through points $(0,0,0)$ and $(x,y,z)$.
\item If $\dim U=2$, then there exists a vector $v=(v_1,v_2,v_3), w=(w_1,w_2,w_3)$ in $\mathbb{R}^3$ such that\[
U=\text{span}(v,w).
\]Geometrically, since the list $v,w$ is linearly independent, $v$ and $w$ are not on the same line in $\mathbb{R}^3$. Hence $U$ is a plane in $\mathbb{R}^3$ that passes the following three points: $(v_1,v_2,v_3), (w_1,w_2,w_3)$ and $(0,0,0)$. 
\item If $\dim U=3$, then Exercise 2.C.1 implies that $U=\mathbb{R}^3$.
\end{enumerate}
\end{proof}

\backmatter
\bibliographystyle{amsalpha}
\bibliography{minqi_s_solutions_to_the_exercises_of_sheldon_axler_2014_linear_algebra_done_right_3rd_edition}
\end{document}
